Baseline centering problem

### 2018-11-10 paper/advup_uniquesol.tex

>>>>

\paragraph{Sampling $\tilde s$ from a single trajectory.} Given a
trajectory $(s_t)$ from any policy, we can keep online a set of unbiased
samples of the trajectory, as follows. Just maintain a set of $k$ past
states with the following replacement rule: at time $t$, with probability
$k/t$, replace one of the previous states with the current state $s_t$.
